This page and the next page should be removed

### 2021-01-17 analysis/manuscript.Rmd
remove messages from tables, add latex packages to dockerfile

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
  - id            : "2"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
  - id            : "3"
    institution   : "Fachhochschule des Mittelstands, Bamberg, Germany"

@@

@@

# # Define function to compute grand averages per condition
# def compute_evokeds(epochs):
#     evokeds = dict(); evokeds_dat = dict()
#     # Each part becomes a dictionary of conditions
#     for pt in ['I', 'II', 'III']:
#         evokeds[pt] = dict(); evokeds_dat[pt] = dict()
#         # Each condition becomes a list of participants
#         for cn in ['Informed', 'Naive']:
#             evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
#             # For every participant we average trials separately for all parts and conditions
#             for vp in epochs.metadata['participant'].unique():
#                 query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
#                 evokeds[pt][cn].append(epochs[query].average())
#             # Compute grand averages across participants for this part and condition
#             evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
#             # Export only the actual data for R
#             evokeds_dat[pt][cn] = evokeds[pt][cn].data
#     return (evokeds, evokeds_dat)

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  #summarise(across(.fns = mean)) %>%
  #pivot_longer(cols = everything(), names_to = "condition", values_to = "objects") %T>%
  write_tsv("analysis/export/exp1-objects.tsv")

# Define global parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = 221, mismatch = 222),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gavgs.RDS")
```

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# # For debugging
# epochs_exp1 <- py$mne$read_epochs("analysis/export/exp1-epo.fif")

# Compute average number of objects per condition
(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

@@

# Load sample time points and electrode montage
times <- scan("analysis/export/sample_times.tsv", quiet = TRUE)
montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")

@@

  require(magick)

@@

# Create a combined legend and colorbar
plot_legends_erps <- function(direction) {
  if (direction == "vertical") {
    mar <- margin(l = 12, r = 10, b = 6, t = 7); vjust <- 3.5
  }
  else {
    mar <- margin(l = 8, r = 12, b = 4, t = 6); vjust <- 0.7
  }
  get_legend(
    tibble(amplitude = c(-1, 1), condition = c("Informed", "Naive")) %>%
      ggplot(aes(x = 0, y = 0, color = condition, fill = amplitude)) +
      geom_line() +
      geom_raster() +
      labs(color = "Conditions", fill = "Informed - naive (µV)") +
      scale_color_viridis_d(begin = 0.1, end = 0.5, guide = guide_legend(direction = "vertical", title.position = "top")) +
      scale_fill_viridis_c(guide = guide_colorbar(direction = "horizontal", ticks = FALSE, title.position = "top", title.vjust = vjust)) +
      theme(
        legend.direction = direction,
        legend.box = direction,
        legend.box.background = element_rect(colour = "black", size = 0.5),
        legend.box.margin = mar,
        legend.background = element_blank(),
        legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
        legend.text = element_text(family = "Helvetica", size = 10),
        legend.key = element_rect(fill = NA),
        legend.key.width = unit(0.7, "cm"),
        legend.key.height = unit(0.4, "cm"),
        legend.spacing.x = unit(0.3, "cm")
      )
  )
}

@@

```{r exp1-table, include=TRUE, results="asis"}
# Define function to print ANOVA-style table
create_table <- function(models, stub_anova, stub_contrasts, caption, note) {
  anov <- map(models, function(model) {
    data.frame(
      "f" = format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2),
      "df" = paste0("(", model$anova$NumDF, ", ", format(round(model$anova$DenDF, 1), trim = TRUE, nsmall = 1), ")"),
      "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(c(stub_anova))
  })
  anov_print <- anov %>%
    map(unite, col = fdf, f, df, sep = " ") %>%
    map(add_row, fdf = "\\textit{F} (\\textit{df})", p = "\\textit{p}", .before = 1) %>%
    bind_cols() %>%
    set_rownames(c("\\textit{Fixed effects}", stub_anova))
  anov %<>% 
    bind_cols() %>% 
    set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_"))
  conts <- map(models, function(model) {
    data.frame(
      "est" = format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2),
      "ci" = paste0(
        "[", format(round(model$contrasts$lower.CL, 2), trim = TRUE, nsmall = 2), ", ",
        format(round(model$contrasts$upper.CL, 2), trim = TRUE, nsmall = 2), "]"
      ),
      "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(stub_contrasts)
  })
  conts_print <- conts %>%
    map(unite, col = estci, est, ci, sep = " ") %>%
    map(add_row, estci = "Est. [95% CI]", p = "\\textit{p}", .before = 1) %>%
    bind_cols() %>%
    set_rownames(c("\\textit{Informed $-$  naive}", stub_contrasts))
  conts %<>% 
    bind_cols() %>% 
    set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
  cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1, ]))
  list(anov_print[2:nrow(anov_print), ], conts_print) %>%
    map(set_colnames, paste0("V", 1:ncol(anov_print))) %>%
    apa_table(
      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N170}" = 4:5, "\\textbf{N400}" = 6:7),
      midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
      caption = caption, note = note
    ) %>% cat()
  return(list("anov" = anov, "conts" = conts))
}

@@

```{r exp2-preparation}
# Read behavioral data for Experiment 2
data_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition
(objects_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
```

```{python exp2-preprocessing}
# List raw EEG filenames
fnames_exp2 = sorted(glob.glob("data/exp2/EEG/*.vhdr"))

# Import behavioral data from R
metadata_exp2 = r.data_exp2

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists("analysis/export/exp2-epo.fif"):
    # Read preprocessed data from file
    epochs_exp2 = mne.read_epochs("analysis/export/exp2-epo.fif", preload=True)
else:
    # Preprocess EEG data for Experiment 2
    epochs_exp2 = [
        preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)
    ]
    # Combine epochs into a single data set
    epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
    # Backup epochs to the export folder
    epochs_exp2.save("analysis/export/exp2-epo.fif")

# Compute grand averages for Experiment 2
evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
```

```{r exp2-analysis}
# Re-import behavioral data and re-factorize some columns
data_exp2 <- py$epochs_exp2$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III")),
  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
  participant = factor(participant),
  item = factor(item)
)

# Check number of rejected epochs
rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
mean(rejected_exp2)    # Mean
median(rejected_exp2)  # Median
range(rejected_exp2)   # Range

# Check if single-trial ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp2-erps.RDS")) {
  # Read data from file
  data_exp2 <- readRDS("analysis/export/exp2-erps.RDS")
} else {
  # Compute single-trial ERPs for Experiment 2
  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp2$get_data(), els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp2, .) %T>%
    saveRDS("analysis/export/exp2-erps.RDS")
}

# Remove the epochs to free up memory
py_run_string("del epochs_exp2")
import("gc")$collect()

# Remove any trials excluded from conditions
data_exp2 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()

# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp2-stats.RDS")) {
  # Read models from file
  models_exp2 <- readRDS("analysis/export/exp2-stats.RDS")
} else {
  # Compute LMMs for Experiment 2
  models_exp2 <- map(
    comps$name,
    compute_models,
    formula = form_exp12,
    data = data_exp2,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp2-stats.RDS")
}
```

@@

@@

@@

# Create plot for Experiment 2
plot_grid(
  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
```

@@

As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`.

@@

```{r joint-analysis}
# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
data_joint <- data_exp2 %>%
  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
  bind_rows(data_exp1, ., .id = "experiment") %>%
  mutate(experiment = as_factor(experiment))

# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
contrasts(data_joint$experiment) <- MASS::ginv(contrasts_experiment)
contrasts(data_joint$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_joint$part) <- MASS::ginv(contrasts_part)

@@

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/joint-stats.RDS")) {
  # Read models from file
  models_joint <- readRDS("analysis/export/joint-stats.RDS")
} else {
  # Compute LMMs for Experiments 1 and 2 combined
  models_joint <- map(
    comps$name,
    compute_models,
    formula = form_joint,
    data = data_joint,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/joint-stats.RDS")
}
```

```{r joint-table, include=TRUE, results="asis"}
# Create table of models for Experiments 1 and 2 combined
table_joint <- create_table(
  models_joint,
  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
  caption = "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
)
```

@@

# Create violin plot for Experiments 1 and 2 combined
plot_grid(
  plot_headings(spacing = c(10, 2, 10, 2, 10)),
  plot_violins(data = data_joint, models = models_joint),
  nrow = 2, rel_heights = c(0.3, 6.7)
) %>% plot_grid(
  plot_legends_violins(),
  nrow = 1, rel_widths = c(8.5, 1.5)
) + # Add some lines (to separate the parts)
  annotate(geom = "segment", x = 11/34*0.85, xend = 11/34*0.85, y = -Inf, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 23/34*0.85, xend = 23/34*0.85, y = -Inf, yend = Inf, linetype = "dashed")
```

@@

```{r control-analysis}
# Calculate average number of objects per condition in Experiments 1 and 2
stims_joint <- (objects_exp1 + objects_exp2) / 2

# Re-load saved ERPs from Experiments 1 and 2
data_joint_control <- bind_rows(
  readRDS("analysis/export/exp1-erps.RDS"),
  readRDS("analysis/export/exp2-erps.RDS") %>%
    mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))),
  .id = "experiment"
) %>% mutate(experiment = as_factor(experiment))

# # Keep all three conditions
# data_joint_control %<>% filter(condition %in% c("Informed", "Naive", "Excl_informed")) %>% droplevels()
# contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
#                                c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)))
# contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
# model_joint_control_N170 <- buildmer::buildmer(
#   N170 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
#   REML = FALSE,
#   control = ctrl_params,
#   buildmerControl = buildmer::buildmerControl(
#     data = data_joint_control,
#     direction = c("order", "backward"),
#     elim = function(logp) exp(logp) >= .20,
#     calc.anova = TRUE,
#     ddf = "Satterthwaite"
#   )
# )
# emmeans::emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
# emmeans::emmeans(model_joint_control_N170@model, pairwise ~ condition | part, infer = TRUE)$contrasts

# This time, we keep only the two conditions with matching keywords
data_joint_control %<>% filter(condition %in% c("Informed", "Excl_informed")) %>% droplevels()

@@

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/joint-control-stats.RDS")) {
  # Read models from file
  models_joint_control <- readRDS("analysis/export/joint-control-stats.RDS")
} else {
  # Re-compute LMMs for Experiments 1 and 2 combined
  models_joint_control <- map(
    comps$name,
    compute_models,
    formula = form_joint,
    data = data_joint_control,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/joint-control-stats.RDS")
}

@@

\setlength{\cslhangindent}{0.5in}

>>>>

affiliation:
  - id            : "1"
    institution   : "Humboldt-Universität zu Berlin"
  - id            : "2"
    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences"
  - id            : "3"
    institution   : "Fachhochschule des Mittelstands"

@@

# Do you want to run the analysis for Experiment 3?
run_exp3 <- FALSE

@@

@@

# Define global parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gavgs.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("analysis/export/exp1-objects.tsv")
```

```{r exp1-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
```

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load sample time points and electrode montage
times <- scan("analysis/export/sample_times.tsv", quiet = TRUE)
montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())

@@

  suppressMessages(require(magick))

@@

# Create a combined legend and colorbar
plot_legends_erps <- function(direction) {
  if (direction == "vertical") {
    mar <- margin(l = 12, r = 10, b = 6, t = 7); vjust <- 3.5
  }
  else {
    mar <- margin(l = 8, r = 12, b = 4, t = 6); vjust <- 0.7
  }
  get_legend(
    tibble(amplitude = c(-1, 0, 1), condition = c("Informed", "Naive", "Informed")) %>%
      ggplot(aes(x = 0, y = 0, color = condition, fill = amplitude)) +
      geom_line() +
      geom_raster() +
      labs(color = "Conditions", fill = "Informed - naive (µV)") +
      scale_color_viridis_d(begin = 0.1, end = 0.5, guide = guide_legend(direction = "vertical", title.position = "top")) +
      scale_fill_viridis_c(guide = guide_colorbar(direction = "horizontal", ticks = FALSE, title.position = "top", title.vjust = vjust)) +
      theme(
        legend.direction = direction,
        legend.box = direction,
        legend.box.background = element_rect(colour = "black", size = 0.5),
        legend.box.margin = mar,
        legend.background = element_blank(),
        legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
        legend.text = element_text(family = "Helvetica", size = 10),
        legend.key = element_rect(fill = NA),
        legend.key.width = unit(0.7, "cm"),
        legend.key.height = unit(0.4, "cm"),
        legend.spacing.x = unit(0.3, "cm")
      )
  )
}

@@

```{r exp1-table, include=TRUE, results="asis"}
# Define function to print ANOVA-style table
create_table <- function(models, stub_anova, stub_contrasts, caption, note) {
  anov <- map(models, function(model) {
    data.frame(
      "f" = format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2),
      "df" = paste0("(", model$anova$NumDF, ", ", format(round(model$anova$DenDF, 1), trim = TRUE, nsmall = 1), ")"),
      "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
    ) %>%
      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
      set_rownames(c(stub_anova))
  })
  suppressMessages(
    anov_print <- anov %>%
      map(unite, col = fdf, f, df, sep = " ") %>%
      map(add_row, fdf = "\\textit{F} (\\textit{df})", p = "\\textit{p}", .before = 1) %>%
      bind_cols() %>%
      set_rownames(c("\\textit{Fixed effects}", stub_anova))
  )
  suppressMessages(
    anov %<>%
      bind_cols() %>%
      set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_"))
  )
  conts <- map(models, function(model) {
    data.frame(
      "est" = format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2),
      "ci" = paste0(
        "[", format(round(model$contrasts$lower.CL, 2), trim = TRUE, nsmall = 2), ", ",
        format(round(model$contrasts$upper.CL, 2), trim = TRUE, nsmall = 2), "]"
      ),
      "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
    ) %>%
      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
      set_rownames(stub_contrasts)
  })
  suppressMessages(
    conts_print <- conts %>%
      map(unite, col = estci, est, ci, sep = " ") %>%
      map(add_row, estci = "Est. [95% CI]", p = "\\textit{p}", .before = 1) %>%
      bind_cols() %>%
      set_rownames(c("\\textit{Informed $-$  naive}", stub_contrasts))
  )
  suppressMessages(
    conts %<>%
      bind_cols() %>%
      set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
  )
  cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1, ]))
  list(anov_print[2:nrow(anov_print), ], conts_print) %>%
    map(set_colnames, paste0("V", 1:ncol(anov_print))) %>%
    apa_table(
      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N170}" = 4:5, "\\textbf{N400}" = 6:7),
      midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
      caption = caption, note = note
    ) %>%
    cat()
  return(list("anov" = anov, "conts" = conts))
}

@@

@@

```{r exp2-preproc, eval=rerun_preproc}
# Read behavioral data for Experiment 2
list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp2

# Apply the preprocessing function for Epxeriment 2 in Python
map2(
  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp2,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp2

# Backup epochs to the export folder
epochs_exp2$save("analysis/export/exp2-epo.fif")

# Apply the function to compute mean ERP amplitudes for Experiment 2
pmap_dfc(comps, compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  # Bind to the behavioral data
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  # Backup to the export folder
  write_tsv("analysis/export/exp2-erps.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp2-gavgs.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("analysis/export/exp2-objects.tsv")
```

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

# Apply these contrasts to the factors in the data
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

# Apply the function to compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp2-mods.RDS") -> models_exp2
```

```{r exp2-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp2)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

# Check number of rejected epochs
data_exp2 %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n) -> rejected_exp2
mean(rejected_exp2)    # Mean
median(rejected_exp2)  # Median
range(rejected_exp2)   # Range

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("analysis/export/exp2-gavgs.RDS")
models_exp2 <- readRDS("analysis/export/exp2-mods.RDS")
```

@@

# Create plot for Experiment 2
plot_grid(
  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
```

@@

@@

As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.

@@

```{r joint-import}
# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
data_exp2 %>%
  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
  bind_rows(data_exp1, ., .id = "experiment") %>%
  mutate(experiment = as_factor(experiment)) -> data_joint

# Subset only the relevant conditions
data_joint %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_joint_subs
```

```{r joint-models, eval=rerun_models}
# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
contrasts(data_joint_subs$experiment) <- MASS::ginv(contrasts_experiment)
contrasts(data_joint_subs$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_joint_subs$part) <- MASS::ginv(contrasts_part)

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-mods.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("analysis/export/joint-mods.RDS")

# Create table of models for Experiments 1 and 2 combined
table_joint <- create_table(
  models_joint,
  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
  caption = "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
)
```

@@

# Create violin plot for Experiments 1 and 2 combined
plot_grid(
  plot_headings(spacing = c(10, 2, 10, 2, 10)),
  plot_violins(data = data_joint_subs, models = models_joint),
  nrow = 2, rel_heights = c(0.3, 6.7)
) %>% plot_grid(
  plot_legends_violins(),
  nrow = 1, rel_widths = c(8.5, 1.5)
) + # Add some lines (to separate the parts)
  annotate(geom = "segment", x = 11/34*0.85, xend = 11/34*0.85, y = -Inf, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 23/34*0.85, xend = 23/34*0.85, y = -Inf, yend = Inf, linetype = "dashed")
```

@@

```{r control-models, eval=rerun_models}
# # Keep all three conditions
# data_joint_control %<>% filter(condition %in% c("Informed", "Naive", "Excl_informed")) %>% droplevels()
# contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
#                                c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)))
# contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
# model_joint_control_N170 <- buildmer::buildmer(
#   N170 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
#   REML = FALSE,
#   control = ctrl_params,
#   buildmerControl = buildmer::buildmerControl(
#     data = data_joint_control,
#     direction = c("order", "backward"),
#     elim = function(logp) exp(logp) >= .20,
#     calc.anova = TRUE,
#     ddf = "Satterthwaite"
#   )
# )
# emmeans::emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
# emmeans::emmeans(model_joint_control_N170@model, pairwise ~ condition | part, infer = TRUE)$contrasts

# This time, we keep only the two conditions with matching keywords
data_joint %>%
  filter(condition %in% c("Informed", "Excl_informed")) %>%
  droplevels() -> data_joint_control

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-control-mods.RDS") -> models_joint_control
```

```{r control-table}
# Calculate average number of objects per condition in Experiments 1 and 2
(stims_joint <- (objects_exp1 + objects_exp2) / 2)

# Load linear mixed models
models_joint_control <- readRDS("analysis/export/joint-control-mods.RDS")

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
<div id="refs" custom-style="Bibliography"></div>
\endgroup
